---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Scholar Navi

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

With the Scholar Navi app you can browse and visualise the data from Google Scholar. The app is written in R/Shiny and takes advantage of the [scholar](https://cran.r-project.org/web/packages/scholar/index.html) R package.

The app displays:

- the citation history of a researcher,
- the citation history of researcher's top publications,
- the co-author network,
- the citation history of a collection of papers (stored in a Google Docs spreadsheet),
- a comparison between researchers.

## Installation

You can install the development version of the Scholar Navi app in R like so:

``` r
library(devtools)
devtools::install_github("dmattek/shiny-scholar-navi")
```

## Running the app

To run the app, type:

```{r example}
library(scholarNaviApp)
scholarNaviApp::run_app()
```
